---
title: "Introduction_mutVis"
author: "Angela Wong"
date: "`r format(Sys.time(), '%d %b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_mutVis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mutVis)
```


# Overview

mutVis is a R package that compares the sequence of an unknown or mutated protein with a set of known protein sequences, finds the best matched ones, and plots the amino acid differences on a graph.


# Installation

mutVis is available on Gihub at https://github.com/angelawong1526/mutVis

``` {r eval=FALSE}
# install.packages("devtools")
library(devtools)
install_github("angelawong1526/mutVis")
library("mutVis")
```
To run the shinyApp:
```{r eval=FALSE}
runMutVisApp()
```
To open the vignette in R:
```{r eval=FALSE}
browseVignettes("mutVis")
```


# Introduction to `mutVis`

This package requires `seqinr, ggplot2, reshape, and utils` to be able to run.
```{r eval=FALSE}
library(seqinr)
library(ggplot2)
library(reshape)
library(utils)
```

### Example Usage of `matchProt()`

```{r fig.width=9, fig.height=6}
unknownProt <- "MAVLILVLLAVVILQAAPIRKLEDLLPTRYPPDHELVYWCTYANQCDFCWECVHGICRNRIQADWPVIHQNDWIINCTVSRWNGICSYYEGPRNHTDHQMDCANPTSHTYPHREYMKIYERDDL"
minPercent <- 95
result <- matchProt(unknownProt, minMatch = minPercent)
result
```


# Licencing

`mutVis` is licensed under the MIT licence.
- Citation: Wong, A (2020). mutVis. R. Retrieved from https://github.com/angelawong1526/mutVis.


# References

Charif, D. and Lobry, J.R. (2007). seqinr. https://cran.r-project.org/web/packages/seqinr/index.html
R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. https://www.R-project.org/
Wickham, H. and Bryan, J. (2019). R Packages (2nd edition). Newton, Massachusetts: O’Reilly Media. https://r-pkgs.org/

## Acknowledgements

This package was developed as part of an assessment for 2020 BCB410H: Applied Bioinformatics, University of Toronto, Toronto, CANADA.
